---
title: "sleep_weight_correlation"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = "~/R/google_data_anlytics_casestudy-2/")
```

## Sleep Vs Weight

Let's find the correlation between sleep and relative body weight(BMI).

First import the necessary data from respective csv files.
```{r warning=FALSE}
library(tidyverse,quietly = TRUE)
weightinf = read_csv("fitbitdat/weightLogInfo_merged.csv")
sleepday = read_csv("fitbitdat/sleepDay_merged.csv")
```
Let's get some basic info about the data we just imported.

```{r}
weightinf$Id = as.character(weightinf$Id)
sleepday$Id = as.character(sleepday$Id)
print(head(sleepday))
print(head(weightinf))
print(summary(sleepday))
print(summary(weightinf))

```


```{r}
print(unique(sleepday$TotalSleepRecords))
```
`TotalSleepRecords` is probably the number of time the user is getting asleep on a day.

First we will aggregate the sleep data by the ID taking the median of variables.


```{r}
sleepday2 <- group_by(sleepday,Id) %>% 
  summarise(AverangeOfTotalBedTime = median(TotalTimeInBed),
            MedianOfTotalSleepTime = median(TotalMinutesAsleep),
            MedianOfTotalSleepRecords = median(TotalSleepRecords),
            Recordstaken=n())
head(sleepday2)
```

Now let's move to weight data to aggregate by ID taking 
```{r}
weightinf2 <- group_by(weightinf,Id) %>%
  summarise(MedianBMI = median(BMI),
            RecordsTaken = n()
  )
head(weightinf2)
```


Here we will perform an inner join(merge the two tables when both table share a common variable) between `sleepday2` and `weightinf2`.

```{r}
df = merge(x=sleepday2[,c(1:4)],y=weightinf2[,c(1,2)],by="Id")
head(df)
```

We will now plot a line graph showing the relationship among the variables.

```{r}
ggplot(data=df)+geom_line(mapping = aes(x=AverangeOfTotalBedTime,
  y=MedianBMI))+ geom_line(mapping = aes(x=MedianOfTotalSleepTime,
                                y=MedianBMI))
```

```{r}
print(cor(df$AverangeOfTotalBedTime,df$MedianBMI))
print(cor(df$MedianOfTotalSleepTime,df$MedianBMI))
print(cor(df$MedianOfTotalSleepRecords,df$MedianBMI))
```
